Manuscript_physiological_consequences_blood_parasite_infection

### 2022-01-24 MS_physiology_infection.Rmd
Add files via upload

treatment_prevalence_changes=ggplot(tab_cont)+
  aes(Timepoint,Count,fill=Prevalence)+
  facet_wrap(facets = "Treatment")+
  geom_bar(stat = 'identity',  width = 0.3)+
  labs(y="Count of nestlings")+
  geom_text(aes(label=Count),position = position_stack(0.5))+
  scale_fill_manual(values=c("#D0D0D0","#A8A8A8"))+
  theme(axis.title.x = element_blank(), strip.text = element_text(size=14, face="bold"),legend.text = element_text(size=12), legend.title = element_text(size=14),axis.title.y=element_text(size=14, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12))

@@

treatment_meaninf_changes=ggplot(tab_mean)+
  aes(Timepoint,Mean_infection_intensity,group=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  ylim(c(0,3))+
  geom_line(aes(color=Treatment), size=2)+
  geom_errorbar(ymin=tab_mean$Mean_infection_intensity-tab_mean$se_inf_int, ymax=tab_mean$Mean_infection_intensity+tab_mean$se_inf_int,colour="black",
               size=1.5 , width=0.05)+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5)+ 
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=12), legend.title = element_text(size=14), axis.title.y=element_text(size=16, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), plot.margin = unit(c(0,0,0,30), "pt"))

@@

### Host health to parasitemia 
```{r, warning=F,message=F}

@@

>>>>

treatment_prevalence_changes=ggplot(tab_cont)+
  aes(Timepoint,Count,fill=Prevalence)+
  facet_wrap(facets = "Treatment")+
  geom_bar(stat = 'identity',  width = 0.3)+
  labs(y="Count of nestlings")+
  geom_text(aes(label=Count),position = position_stack(0.5))+
  scale_fill_manual(values=c("#D0D0D0","#A8A8A8"))+
  theme(axis.title.x = element_blank(), strip.text = element_text(size=16, face="bold"),legend.text = element_text(size=14), legend.title = element_text(size=16),axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16))

@@

treatment_meaninf_changes=ggplot(tab_mean)+
  aes(Timepoint,Mean_infection_intensity,group=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  ylim(c(0,3))+
  geom_line(aes(color=Treatment), size=2)+
  geom_errorbar(ymin=tab_mean$Mean_infection_intensity-tab_mean$se_inf_int, ymax=tab_mean$Mean_infection_intensity+tab_mean$se_inf_int,colour="black",
               size=1.5 , width=0.05)+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5)+ 
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))

@@

# Host health to parasitemia 
```{r, warning=F,message=F}

@@

# Supplementary figure

gg1=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,Breathing_rate)+
  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg2=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,body_temperature)+
  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg3=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,delta_body_condition)+
  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body condition (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg4=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,Growth_rate)+
  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

# Figure S1

gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))
